JEThread: A Thread Pool Implementation in C

### 2018-05-04 thread-pool-implementation/paper.tex

\section{Conclusion}
	A thread pool should be efficient when managing a large number of tasks and executing them concurrently. In JEThread, we use work stealing to facilitate the work throughput by letting idle threads execute other threads' tasks. However, thread pool is not a silver bullet that solves every problem of thread. The overhead of thread context switch is transferred to each thread's task queue as executing tasks requires dequeueing the task each time. We've also conducted experiment with creating only one task queue shared between all threads, but the same thing still applies here that the overhead is transferred to the queue since accessing tasks is performed with lock's protection. In addition, round-robin style task distribution may not be the best way to distribute tasks as calling thread is unaware of the actual workload in its distribution target. The work stealing is also very tricky to implement as the stealer is not aware of the workload distribution during runtime. If the majority of threads finish execution while a few survivor threads with many tasks are still alive, the parallelism can be compromised since a few threads become the bottleneck and cause the main thread waiting unnecessarily. Additional optimization such as runtime dynamic workload check and compiler support for user-guided optimization will further increase the usability of thread pool.\\

>>>>

\section{Conclusion}
	A thread pool should be efficient when managing a large number of tasks and executing them concurrently. In JEThread, we use work stealing to facilitate the work throughput by letting idle threads execute other threads' tasks. However, thread pool is not a silver bullet that solves every problem of thread. The overhead of thread context switch is transferred to each thread's task queue as executing tasks requires dequeueing the task each time. We've also conducted experiment with creating only one task queue shared between all threads, but the same thing still applies here that the overhead is transferred to the queue since accessing tasks is performed with lock's protection. In addition, round-robin style task distribution may not be the best way to distribute tasks as calling thread is unaware of the actual workload in its distribution target. The work stealing is also very tricky to implement as the stealer is not aware of the workload distribution during runtime. If the majority of threads finish execution while a few survivor threads with many tasks are still alive, the parallelism can be compromised since a few threads become the bottleneck and cause the main thread waiting unnecessarily. Additional optimization such as runtime dynamic workload check and compiler support for user-guided optimization will further increase the usability of thread pool.
